Code Overflow: \\ An empirical study of online code reuse

### 2016-08-15 latex/stackoverflow.tex
Added changes from iMac

\begin{table*}[h]
	\centering
	\caption{Qualitas (2013-09-01r): Simian and NiCad clone results}
	\label{t_simian_raw_results}
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
		\hline
		\multirow{4}{*}{Statistics} 
		& \multicolumn{4}{c|}{Simian Default settings} 
		& \multicolumn{4}{c|}{Simian FSE'13 settings}
		& \multicolumn{4}{c|}{Simian Default settings} 
		& \multicolumn{4}{c}{Simian FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
		& \multicolumn{4}{c|}{threshold=6} 
		& \multicolumn{4}{c|}{threshold=5}  
		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
		& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
		& \multicolumn{4}{c|}{rename=none,abstract=none} 
		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
		% \hline
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
		\hline
		%Removed & 11 & -- & -- & -- & 0 & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- \\ %& 11 & -- & -- & -- \\
		Total & 647 & 24,802 & -- & -- &  152 & 7,289,272 & -- & -- & 983 & 106,091 & -- & -- & 8,100 & 31,141,599 & -- & --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
		Mean & -- & 38 & 7.53 & 0.27 & -- & 47,956 & 4.76 & 0.27 & -- & 108 & 9.48 & 0.25 & -- & 3,845 & 5.52 & 0.19 \\ % & -- & 9,356 & 4.74 & 0.26 \\
		Std Dev. & -- & 87 & 3.87 & 0.22 & -- & 433,467 & 0.93 & 0.18 & 	& 200 & 3.04	& 0.18 & -- & 4,305 & 2.49 & 0.15 \\ % & -- & 96,038	& 0.99 & 0.18 \\
		Max & -- & 551 & 63 & 0.94 & -- & 5,278,408 & 8 & 0.83 & -- & 1,816 & 39 & 0.80 & -- & 46,469 & 111 & 0.88\\ % & -- & 7,837,204 & 28 & 0.94 \\
		Min & -- & 1 & 5 & 0.01 & -- & 1 & 4 & 0.01 & -- & 1 & 7 & 0.02 & -- & 1 & 3 & 0.01 \\ % & -- & 1 & 4 & 0.002 \\
		Median & -- & 3 & 7 & 0.22 & -- & 22.5 & 4 & 0.23 & -- & 14 & 8 & 0.19 & -- & 3,095 & 5 & 0.14 \\ % & -- & 27 & 4 & 0.22 \\
		Mode & -- & 1 & 7 & 0.25 & -- & 1 & 4 & 0.50 & -- & 1 & 8 & 0.53 & -- & 1 & 4 & 0.33 \\ % & -- & 1 & 4 & 0.50 \\
		\hline
	\end{tabular} %
}
\end{table*}

\begin{table*}[h]
	\centering
	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (45 new + 18 old Qualitas projects)}
	\label{t_simian_raw_results}
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
		\hline
		\multirow{4}{*}{Statistics} 
		& \multicolumn{4}{c|}{Simian Default settings} 
		& \multicolumn{4}{c|}{Simian FSE'13 settings} 
		& \multicolumn{4}{c|}{NiCad Default settings} 
		& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
		& \multicolumn{4}{c|}{threshold=6} 
		& \multicolumn{4}{c|}{threshold=5} 
		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
		& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
		& \multicolumn{4}{c|}{rename=none,abstract=none} 
		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
		% \hline
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
		\hline
		%Removed & 11 	& -- 	& -- 	& -- 	& 0 & -- & -- & -- \\ %& 11 & -- & -- & -- \\
		Total 	& 789 	& 61,164 & -- 	& -- 	&  170 	& 11,915,544 & -- 	& --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
		Mean 	& -- 	& 78 	& 7.32 	& 0.26 	& -- 	& 70,091 	& 4.76 	& 0.29 \\ % & -- & 9,356 & 4.74 & 0.26 \\
		Std Dev. & -- 	& 208 	& 2.71 	& 0.21 	& -- 	& 703,788 	& 0.89 	& 0.19 \\ % & -- & 96,038	& 0.99 & 0.18 \\
		Max 	& -- 	& 1,300 & 49 	& 0.94 	& -- 	& 9,065,774 & 9		& 0.83 \\ % & -- & 7,837,204 & 28 & 0.94 \\
		Min 	& -- 	& 1 	& 5 	& 0.01 	& -- 	& 1 		& 4 	& 0.01 \\ % & -- & 1 & 4 & 0.002 \\
		Median 	& -- 	& 2 	& 7 	& 0.20 	& -- 	& 17 		& 5 	& 0.26 \\ % & -- & 27 & 4 & 0.22 \\
		Mode 	& -- 	& 1 	& 7 	& 0.33 	& -- 	& 1 		& 4 	& 0.33 \\ % & -- & 1 & 4 & 0.50 \\
		\hline
	\end{tabular} %
}
\end{table*}

\begin{table*}[h]
	\centering
	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (only 45 new Qualitas projects)}
	\label{t_simian_raw_results}
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
			\hline
			\multirow{4}{*}{Statistics} 
			& \multicolumn{4}{c|}{Simian Default settings} 
			& \multicolumn{4}{c|}{Simian FSE'13 settings} 
			& \multicolumn{4}{c|}{NiCad Default settings} 
			& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
			& \multicolumn{4}{c|}{threshold=6} 
			& \multicolumn{4}{c|}{threshold=5} 
			& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
			& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
			& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
			& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
			& \multicolumn{4}{c|}{rename=none,abstract=none} 
			& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
			% \hline
			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
			\hline
			%Removed & 11 	& -- 	& -- 	& -- 	& 0 & -- & -- & -- \\ %& 11 & -- & -- & -- \\
			Total 	& 736 	& 60,678 & -- 	& -- 	&  166 	& 10,273,534 & -- 	& --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
			Mean 	& -- 	& 82 	& 7.26 	& 0.26 	& -- 	& 61,889 	& 4.77 	& 0.28 \\ % & -- & 9,356 & 4.74 & 0.26 \\
			Std Dev. & -- 	& 214 	& 2.24 	& 0.21 	& -- 	& 607,074 	& 0.89 	& 0.18 \\ % & -- & 96,038	& 0.99 & 0.18 \\
			Max 	& -- 	& 1,298 & 32 	& 0.94 	& -- 	& 7,720,970 & 9		& 0.83 \\ % & -- & 7,837,204 & 28 & 0.94 \\
			Min 	& -- 	& 1 	& 5 	& 0.01 	& -- 	& 1 		& 4 	& 0.01 \\ % & -- & 1 & 4 & 0.002 \\
			Median 	& -- 	& 2 	& 7 	& 0.20 	& -- 	& 16.5 		& 5 	& 0.26 \\ % & -- & 27 & 4 & 0.22 \\
			Mode 	& -- 	& 1 	& 7 	& 0.33 	& -- 	& 1 		& 4 	& 0.33 \\ % & -- & 1 & 4 & 0.50 \\
			\hline
		\end{tabular} %
	}
\end{table*}

>>>>

\begin{table*}[h]
	\centering
	\caption{Qualitas (2013-09-01r): Simian and NiCad clone results}
	\label{t_simian_raw_results}
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
		\hline
		\multirow{4}{*}{Statistics} 
		& \multicolumn{4}{c|}{Simian Default settings} 
		& \multicolumn{4}{c|}{Simian FSE'13 settings}
		& \multicolumn{4}{c|}{NiCad Default settings} 
		& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} 
		& \multicolumn{4}{c|}{threshold=6} 
		& \multicolumn{4}{c|}{threshold=5}  
		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\ 
		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
		& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
		& \multicolumn{4}{c|}{rename=none,abstract=none} 
		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ 
		\hline
		Total	   & 654 & 24,929 & -- & -- &  1,175 & 16,957,362 & -- & -- & 983 & 106,091 & -- & -- & 8,100 & 31,141,599 & -- & --  \\ 
		Mean	  & -- & 38 & 7.54 & 0.27 & -- & 14,444 & 4.80 & 0.28 & -- & 108 & 9.48 & 0.25 & -- & 3,845 & 5.52 & 0.19 \\ 
		Std Dev. & -- & 87 & 3.21 & 0.22 & -- & 281,747 & 1.22 & 0.18 & 	& 200 & 3.04	& 0.18 & -- & 4,305 & 2.49 & 0.15 \\
		Max        & -- & 551 & 49 & 0.94 & -- & 9,599,676 & 18 & 0.89 & -- & 1,816 & 39 & 0.80 & -- & 46,469 & 111 & 0.88\\ 
		Min        & -- & 1 & 5 & 0.01 & -- & 1 & 4 & 0.02 & -- & 1 & 7 & 0.02 & -- & 1 & 3 & 0.01 \\ 
		Median  & -- & 3 & 7 & 0.23 & -- & 22 & 5 & 0.24 & -- & 14 & 8 & 0.19 & -- & 3,095 & 5 & 0.14 \\ 
		Mode    & -- & 1 & 7 & 0.25 & -- & 1 & 4 & 0.50 & -- & 1 & 8 & 0.53 & -- & 1 & 4 & 0.33 \\ 
		\hline
	\end{tabular} %
}
\end{table*}

\begin{table*}[h]
	\centering
	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (44 new + 19 old Qualitas projects)}
	\label{t_simian_raw_results}
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
		\hline
		\multirow{4}{*}{Statistics} 
		& \multicolumn{4}{c|}{Simian Default settings} 
		& \multicolumn{4}{c|}{Simian FSE'13 settings} 
		& \multicolumn{4}{c|}{NiCad Default settings} 
		& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
		& \multicolumn{4}{c|}{threshold=6} 
		& \multicolumn{4}{c|}{threshold=5} 
		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
		& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
		& \multicolumn{4}{c|}{rename=none,abstract=none} 
		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
		% \hline
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
		\hline
		%Removed & 11 	& -- 	& -- 	& -- 	& 0 & -- & -- & -- \\ %& 11 & -- & -- & -- \\
		Total 	& 789 	& 61,164 & -- 	& -- 	&  170 	& 11,915,544 & -- 	& --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
		Mean 	& -- 	& 78 	& 7.32 	& 0.26 	& -- 	& 70,091 	& 4.76 	& 0.29 \\ % & -- & 9,356 & 4.74 & 0.26 \\
		Std Dev. & -- 	& 208 	& 2.71 	& 0.21 	& -- 	& 703,788 	& 0.89 	& 0.19 \\ % & -- & 96,038	& 0.99 & 0.18 \\
		Max 	& -- 	& 1,300 & 49 	& 0.94 	& -- 	& 9,065,774 & 9		& 0.83 \\ % & -- & 7,837,204 & 28 & 0.94 \\
		Min 	& -- 	& 1 	& 5 	& 0.01 	& -- 	& 1 		& 4 	& 0.01 \\ % & -- & 1 & 4 & 0.002 \\
		Median 	& -- 	& 2 	& 7 	& 0.20 	& -- 	& 17 		& 5 	& 0.26 \\ % & -- & 27 & 4 & 0.22 \\
		Mode 	& -- 	& 1 	& 7 	& 0.33 	& -- 	& 1 		& 4 	& 0.33 \\ % & -- & 1 & 4 & 0.50 \\
		\hline
	\end{tabular} %
}
\end{table*}

\begin{table*}[h]
	\centering
	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (only 44 new Qualitas projects)}
	\label{t_simian_raw_results}
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
			\hline
			\multirow{4}{*}{Statistics} 
			& \multicolumn{4}{c|}{Simian Default settings} 
			& \multicolumn{4}{c|}{Simian FSE'13 settings} 
			& \multicolumn{4}{c|}{NiCad Default settings} 
			& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
			& \multicolumn{4}{c|}{threshold=6} 
			& \multicolumn{4}{c|}{threshold=5} 
			& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
			& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
			& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
			& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
			& \multicolumn{4}{c|}{rename=none,abstract=none} 
			& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
			% \hline
			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
			\hline
			%Removed & 11 	& -- 	& -- 	& -- 	& 0 & -- & -- & -- \\ %& 11 & -- & -- & -- \\
			Total 	& 736 	& 60,678 & -- 	& -- 	&  166 	& 10,273,534 & -- 	& --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
			Mean 	& -- 	& 82 	& 7.26 	& 0.26 	& -- 	& 61,889 	& 4.77 	& 0.28 \\ % & -- & 9,356 & 4.74 & 0.26 \\
			Std Dev. & -- 	& 214 	& 2.24 	& 0.21 	& -- 	& 607,074 	& 0.89 	& 0.18 \\ % & -- & 96,038	& 0.99 & 0.18 \\
			Max 	& -- 	& 1,298 & 32 	& 0.94 	& -- 	& 7,720,970 & 9		& 0.83 \\ % & -- & 7,837,204 & 28 & 0.94 \\
			Min 	& -- 	& 1 	& 5 	& 0.01 	& -- 	& 1 		& 4 	& 0.01 \\ % & -- & 1 & 4 & 0.002 \\
			Median 	& -- 	& 2 	& 7 	& 0.20 	& -- 	& 16.5 		& 5 	& 0.26 \\ % & -- & 27 & 4 & 0.22 \\
			Mode 	& -- 	& 1 	& 7 	& 0.33 	& -- 	& 1 		& 4 	& 0.33 \\ % & -- & 1 & 4 & 0.50 \\
			\hline
		\end{tabular} %
	}
\end{table*}
